\documentclass[12pt]{report}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

\graphicspath{ {images/} }

\begin{document}


\section{put in the report}

RDS is introduced by Heckathorn 1997.

Many papers try to warn rds users.
Some paper are studying how the violation of some assumptions can influence on the RDS estimates.

In \cite{gile2010respondent} is studied  the sensitivity to the procedure for selecting the seeds, sensitivity to respondent behavior, sensitivity to the with-replacement assumption.

In order to study we have random graphs where we have some parameters to change. We want the same with values.



IT is written in \cite{gile2010respondent} that V-H estimator outperforms S-H estimator.


Show that energy is less then in random configuration 

[try to sample independenlty but with probabilities pi and look at the variance. is it the same, i think no].



!!! compare when reported degree is not correct and using just mean


$B$ - budget

$C_1$ - cost of one step of walk (individuals just provide the correct number of their contacts)

$C_2$ - cost of participation (cost of interview with individuals)

$n$ - number of steps

$m$ - number of participants from $n$

The next equality should be true:

$$B = n \cdot C_1 + m \cdot C_2$$

If we want to skip $k$ steps between taking the node as a participant then
$$B = nC_1 + \frac{n}{k+1}C_2$$

Here $m = \frac{n}{k+1}$ as we take each $k+1$ node as a participant. So having budget $B$ and skipping each $k$ node allows as to perform $n = \frac{(k+1)B}{(k+1)C_1 + C_2}$ steps with $m = \frac{B}{(k+1)C_1 + C_2}$ number of participants.

Then variance:

$$\frac{\sigma^2}{\frac{B}{(k+1)C_1 + C_2}} \frac{1+\rho^{k+1}}{1-\rho^{k+1}}$$ 



Then 
$P^*$ is symmetric [explain why]
$P^*$ is diagonalizable [explain why]
eigenvalues of $P$ and $P^*$ are the same


Function: variance of mean with skipping having fixed budget and payments (general case)
$$ var\left[\bar{X} \right] = \frac{1}{n} \sum_{i=2}^r\frac{1-\lambda_i^2 - 2\frac{\lambda_i}{n} + 2\frac{\lambda_i^{n+1}}{n}}{(1 - \lambda_i)^2} <f, v_i>^2_{\pi}$$



$$ \sigma_{\hat{\mu}}^2(k) = \frac{\sigma^2}{\frac{B}{kC_1 + C_2}} \frac{1+\rho^{k}}{1-\rho^{k}}$$.

$$  \sigma_{\hat{\mu}}^2(k) = \frac{1}{\frac{B}{kC_1 + C_2}} \sum_{i=2}^r\frac{1 + \lambda_i^k}{1 - \lambda_i^k} <g, v_i>^2_{\pi}$$



$$\sigma_{\hat{\mu}}^2 = \frac{\sigma^2}{n} \frac{1+\rho}{1-\rho}$$

$$\sigma_{\hat{\mu}}^2(k) = \frac{\sigma^2}{n} \frac{1+\rho^k}{1-\rho^k}$$


\end{document}